### 2018-08-08 paper/system-model.tex
pass on Sec 2

\name provides a private and fully decentralized file transfer service by exploiting 
%% is a distributed system made of
users' devices.  We assume any two devices can communicate with one
another as soon as one knows the address of the other (\eg using the
Internet, possibly extended with NAT traversal techniques). The
devices owned by the same user (this user's \squad) know of each
other. Other users' devices can help transfer the file from one user
to another but are not needed for storage.  We also assume that users
can exchange some limited amounts of data out-of-band, \ie through
some other channel than the network just mentioned (\eg using \ac{NFC}
or QR codes).
%system model: explain e-squad, contrast with cloud

@@

In the following, we first describe how file transfer typically occurs
when users rely on a cloud storage provider. We use this simple use
case to highlight some of the desirable privacy properties of a file
transfer service, before mapping them into our fully decentralized
(a.k.a. peer-to-peer (P2P\footnote{We use the terms \emph{fully decentralized} and
  \emph{P2P} interchangeably, and preferentially the latter for brevity.}))
context.  We finally consider the additional privacy properties
required to protect users from inferences, such as by network traffic
analysis, and state our adversary model.

@@

The use of the cloud provider, as a third party,
provides two main privacy properties, which we should preserve when
moving to a P2P setting:
\begin{itemize}
\item Alice and Bob are the only users who learn 
about Alice sharing a file with Bob.
\item The composition and behavior of Alice and Bob's \squad remain
  hidden to each other, and to other users. I.e. Alice does not learn
  which devices Bob owns or uses, let alone how Bob uses them, and
  reciprocally.
\end{itemize} 
The cloud provider, however, has this information and any other
stemming from the users' interaction with the service, and can draw
inferences from metadata even when the data itself is encrypted. The
provider thus poses a threat to the users' privacy which we remove in
the P2P scenario~\cite{DevilInMetadata}.

@@

Friendly surveillance can be mitigated by ensuring security properties 
typically associated with onion routing, as defined by Camenisch and Lysyanskaya~\cite{CLOnionRouting}: 
% We combine the requirements from
% the \ac{P2P} setting with those from onion routing for anonymity.
% Camenisch and Lysianskaya \cite{CLOnionRouting} define security properties 
% for onion routing:
\textit{onion-correctness, integrity}, and \textit{security}. %(wrap resistance,
                                %indistinguishability)
Informally, \textit{onion-correctness} means that if an onion is formed
correctly, processed by the correct routers in the correct order, then
the correct message is received by the last router. \textit{Onion-integrity}
means that even for an onion created by an adversary, the path length
is bounded by $N$. \textit{Onion-security} means that an adversary sending an
 onion to a router as a challenge
 and able to see the response (the outcome of how the
onion is processed), cannot distinguish between whether that onion
corresponds to a particular message and route or not. This is also
true for a \emph{re-wrapped} onion, \ie a challenge (onion) wrapped in
another layer. The formal definitions are in~\cite{CLOnionRouting} along
with a theorem that states that an onion routing scheme satisfying
these three properties, combined with secure point-to-point channels,
is universal composability (UC)-secure, \ie the protocol remains
secure even if arbitrarily composed with other instances of the same or other protocols.
These properties cover the concerns about
revealing to others that Alice shares a file with Bob in the first
place. In \name, we additionally derive the property of
\emph{device-unlinkability} from the \ac{P2P} requirements above, meaning that
using \name does not reveal the \squad a device belongs to nor its
owner. Thus, no information on the user's behavior (e.g. being online)
can be infered through \name. 
\sonja{insert more formal definition
  here, and perhaps explanation that we need it because we introduce
  availability information}

>>>>

\name provides a private and fully decentralized file transfer service by exploiting 
%% is a distributed system made of
users' devices.  We assume any pair of devices can communicate with each other as soon as one knows the address of the other (\eg using the
Internet, possibly extended with NAT traversal techniques). The
devices owned by the same user (this user's \squad) know of each
other. We leverage the the devices of other users to help transfer the file from one user
to another, but do not use them for storage.  We also assume that users
can exchange some limited amounts of data out-of-band, \ie through
some other channel than the network just mentioned (\eg using \ac{NFC}
or QR codes).
%system model: explain e-squad, contrast with cloud

@@

In the following, we first describe how file transfer typically occurs
when users rely on a cloud storage provider. We use this simple use
case to highlight some of the desirable privacy properties of a file
transfer service, before mapping them into our fully decentralized
(a.k.a. peer-to-peer, or P2P short short\footnote{We use the terms \emph{fully decentralized} and
  \emph{P2P} interchangeably, and preferentially the latter for brevity.})
context.  We finally consider the additional privacy properties
required to protect users from inferences, such as by network traffic
analysis, and state our adversary model.

@@

The use of the cloud provider, as a third party,
provides two main privacy properties, which we should preserve when
moving to a P2P setting:
\begin{itemize}
\item Alice and Bob are the only users who learn 
about Alice sharing a file with Bob.
\item The composition and behavior of Alice and Bob's \squad{}s remain
  hidden to each other, and to other users. I.e. Alice does not learn
  which devices Bob owns or uses, let alone how Bob uses them, and
  reciprocally.
\end{itemize} 
The cloud provider, however, has this information and any other
stemming from the users' interaction with the service, and can draw
inferences from metadata even when the data itself is encrypted. The
provider thus poses a threat to the users' privacy which we remove in
the P2P scenario~\cite{DevilInMetadata}.

@@

Friendly surveillance can be mitigated by ensuring security properties 
typically associated with onion routing, as defined by Camenisch and Lysyanskaya~\cite{CLOnionRouting}: 
% We combine the requirements from
% the \ac{P2P} setting with those from onion routing for anonymity.
% Camenisch and Lysianskaya \cite{CLOnionRouting} define security properties 
% for onion routing:
\textit{onion-correctness, integrity}, and \textit{security}. %(wrap resistance,
                                %indistinguishability)
Informally, \textit{onion-correctness} means that if an onion is formed
correctly, processed by the correct routers in the correct order, then
the correct message is received by the last router. \textit{Onion-integrity}
means that even for an onion created by an adversary, the path length
is bounded by $N$. \textit{Onion-security} means that an adversary sending an
 onion to a router as a challenge
 and able to see the response (the outcome of how the
onion is processed), cannot distinguish between whether that onion
corresponds to a particular message and route or not. This is also
true for a \emph{re-wrapped} onion, \ie a challenge (onion) wrapped in
another layer. The formal definitions are in~\cite{CLOnionRouting} along
with a theorem that states that an onion routing scheme satisfying
these three properties, combined with secure point-to-point channels,
is universal composability (UC)-secure, \ie the protocol remains
secure even if arbitrarily composed with other instances of the same or other protocols.
These properties cover the concerns about
revealing to others that Alice shares a file with Bob in the first
place. In \name, we additionally derive the property of
\emph{device-unlinkability} from the \ac{P2P} requirements introduced above, meaning that
using \name neither reveals the \squad a device belongs to, nor its
owner. Thus, no information on the user's behavior (e.g. being online)
can be infered through \name. 
\sonja{insert more formal definition
  here, and perhaps explanation that we need it because we introduce
  availability information}
